DraftOne

### 2016-06-13 DraftOne.Rmd
Get everything in DraftOne.Rmd up to `sim_data` running

```{r}
# Function to generate a binary exposure
binary_exposure 
binary_exposure(n = 5, p_exp = 0.25)
```

@@

```{r}
n <- 1000
p_exp <- 0.25
lambda <- 100

x <- binary_exposure(n = n, p_exp = p_exp)
exp_base_y <- constant_baseline(n = n, lambda = lambda)
df <- full_join(x, exp_base_y, by = "date")
```

>>>>

```{r}
# Function to generate a binary exposure
binary_exposure 
binary_exposure(n = 5, p = 0.25)
```

@@

```{r}
n <- 1000
p <- 0.25
lambda <- 100

x <- binary_exposure(n = n, p = p)
exp_base_y <- constant_baseline(n = n, lambda = lambda)
df <- full_join(x, exp_base_y, by = "date")
```
